%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Yuxiang Zhang} % Your name
\address{8800 Biological Grade, La Jolla, CA 92037-0208} % Your secondary addess (optional)
\address{(858) 336-6327 or kimiyuxiang@gmail.com} % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\begin{rSection}{OBJECTIVE} 

To obtain an intern position with analytical and programming skills, with special interests in wave field modeling and near surface imaging.
\end{rSection}


%----------------------------------------------------------------------------------------
%	Summary 
%----------------------------------------------------------------------------------------
 
\begin{rSection}{SUMMARY OF QUALIFICATIONS}  
\begin{itemize}
\item Strong numerical analysis and modeling background.
\item Proficient in programming, including multi-platform programming and parallel computing. 
\item Strong communication, team working and problem solving skills.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{RESEARCH  EXPERIENCE}

\begin{rSubsection}{Marine EM Laboratory,  Scripps Institution of Oceanography
}{09/2013-Present}{Research Assistant}{UC San Diego}
\item Contributed to the first release of MARE3DEM in the annual meeting of SEG, 2014. 
\item Integrated Spectral Bisection Algorithm(C) into the 3D EM modeling package MARE3DEM(Fortran90), using the Intel C and Fortran compilers. 
\item Implemented residual based goal-oriented error estimator to MARE3DEM, improving the accuracy and efficiency.
\item Modularized the computational geometry routine to compute mesh topology information, expediting the stiffness matrix formulation in the finite element modeling process. 
%\item Accelerated the stiffness matrix formulation for the weak form of the discretized Maxwell Equation. 
\item Alleviating the computational expense for MARE3DEM by implementing the longest edge bisection technique as the new mesh refinement engine.
%\item Collaborated with Prof. Jeff Ovall to develop new 3D computational geometry algorithm.
%\item Found a new way to refine the 3D finite element mesh, using the longest edge bisection technique in the Finite Element ToolKit(FETK). 
\item Designed and established the C-Fortran mesh refinement interface between Finite Element ToolKit(FETK) and MARE3DEM, debugging using LLDB. 
\item Collaborate with the Center for Computational Mathematics to integrate Bank and Holst Domain Decomposition Paradigm into MARE3DEM. 
\item Conducted performance analysis for MARE3DEM on the local HPC, with a 3D model including bathymetry and resistive oil reservoir.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{San Diego Supercomputer Center}{06/2013-09/2013}{Research Assistant}{UC San Diego}
\item Performed strong and weak scalability test for the paralleled anelastic 3D wave propagation package(AWP) on Triton Shared Computing Cluster(TSCC). 
\item Completed the performance(Profiling and tracing) analysis of AWP, using TAU on Kraken Cluster. 
%\item Conducted large-scale 3D numerical simulations of seismic wave propagation on the distributed architecture of TSCC.
%\item Established the file I/O interface between AWP and the full-3D waveform tomography package(F3DT) to improve run-time efficiency. 
\item Researched the theory of Full 3D Waveform Tomography and documented the workflow to compile and run F3DT package on Triton Cluster.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Center for Subsurface Imaging and Fluid Modeling
}{02/2012-04/2012}{Research Intern}{King Abdullah Univ. of Sci. and Tech.}

\item Seismic data processing and interpreting, using traveltime and waveform tomography.
\item Participated onshore seismic survey and electromagnetic data acquisition, improved team working and communication skills.
\item Studied seismic interferometry and the theory of seismic imaging.

\end{rSubsection}

\begin{rSubsection}{Institute of Geology and Geophysics}{06/2011-09/2011}{Research Intern}{Chinese Academy of Sciences}

\item Researched and tested the finite difference scheme for elastic wave propagation.
\item Studied the theory of frequency-domain Full Waveform Inversion. 

\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{COMPUTER SKILLS}

{\sl Languages:} 
FORTRAN 90/03, C, C++, CUDA,  MPI and Unix Shell Scripting. \\
{\sl Tools:} 
\quad \quad  Makefile, LLDB, Matlab, Subversion, LaTeX, TracWiki and Vim.
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

{\sl Ph.D.,} Applied Geophysics\\
University of California, San Diego  \hfill 2012-Present \\
Selected courses: AdvTech/Computational Math I/II/III (A+), Parallel Comput.Sci. \& Engineer (A+)
 
 {\sl B.S.,} Applied Geophysics\\
University of Science and Technology of China. \hfill  2008-2012\\
G.P.A   3.7/4.0

 {\sl Visiting Student,} Geology\\
University of G\"{o}ttingen, Germany.    \hfill   09/2011-02/2012\\

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXTRACURRICULAR  ACTIVITIES}

10/2014 \quad SEG annual Meeting, Denver, Volunteering\\
06/2014 \quad UC San Diego PhD Career Conference, Volunteering\\
05/2014 \quad MOCHA marine MT deployment  Oregon Offshore, Volunteering\\	
03/2014 \quad Seafloor Electromagnetic Methods Consortium, Presenting \\
12/2013 \quad American Geophysical Union Annual Meeting, San Fransisco\\
11/2013 \quad Nvidia GPU Workshop, San Diego Supercomputer Center\\
08/2013 \quad Discover Big Data Workshop, SDSC 2013 Summer Institute\\
06/2013 \quad MPI Workshop by  XSEDE, UC Los Angeles\\
06/2013 \quad UCSD Triton 5K Running 

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS AND  AWARDS
%----------------------------------------------------------------------------------------
\begin{rSection}{HONORS AND  AWARDS}

2012  \quad \quad RA Scholarship, UCSD/SDSU\\
2011  \quad \quad Erasmus Scholarship, EACEA\\
2011  \quad \quad Outstanding Student Scholarship, USTC\\
2010  \quad \quad National Aspiration Scholarship.\\
%2010  \quad \quad Outstanding Student Scholarship, USTC\\
2009  \quad \quad Outstanding Student Scholarship, USTC\\
2008  \quad \quad Provincial Champion in Mathmatics, National College Entrance Exam.

\end{rSection}



%----------------------------------------------------------------------------------------
%	PROFESSIONAL SOCIETIES
%----------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL AFFILIATION}
American Geophysical Union \\ Society of Exploration Geophysicists
% \\ UCSD Strides Running Club
%  \\  Association of Scientific Expedition of USTC


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
